A meta-analysis of mental rotation ability in the first years of life

### 2022-04-28 code/analysis.Rmd
Add ICC and hypothesis tests

# Run Bayesian multilevel model
res_brm <- update(res_prior, sample_prior = FALSE)
summary(res_brm)
# plot(res_brm)
```

@@

# Meta-regression with gender, age, and task
res_reg <- rma.mv(
  gi, vi,
  mods = ~ gender * age_c + task,
  random = ~ 1 | article / experiment,
  data = dat_reg,
  slab = experiment
)
print(res_reg)
# forest(res_full)
```

>>>>

# Run Bayesian multilevel model
res_brm <- update(res_prior, sample_prior = FALSE)
summary(res_brm)
# plot(res_brm)

# Compute intra-class correlation
sd_article <- VarCorr(res_brm)$article$sd
sd_experiment <- VarCorr(res_brm)$`article:experiment`$sd
(icc <- sd_article / (sd_article + sd_experiment))

# Compute probabilities of the meta-analytic being greater than 0
hypothesis(res_brm, "Intercept > 0")$hypothesis
```

@@

# Meta-regression with gender, age, and task
res_reg <- rma.mv(
  gi, vi,
  mods = ~ gender * age_c + task,
  random = ~ 1 | article / experiment,
  data = dat_reg,
  slab = experiment
)
print(res_reg)
# forest(res_full)

# Compute intra-class correlation
sd_article_reg <- VarCorr(res_brm_reg)$article$sd
sd_experiment_reg <- VarCorr(res_brm_reg)$`article:experiment`$sd
(icc_reg <- sd_article_reg / (sd_article_reg + sd_experiment_reg))

# Compute reduction in heterogeneity compared to the original meta-analysis
1 - (sd_article_reg + sd_experiment_reg) / (sd_article + sd_experiment)

# Compute probabilities of the different effects being greater than 0
hypothesis(res_brm_reg, "gender3M2 > 0")$hypothesis
hypothesis(res_brm_reg, "gender2M1 < 0")$hypothesis
hypothesis(res_brm_reg, "task2M1 > 0")$hypothesis
```
